Analysis-ready VCF at Biobank scale using Zarr

### 2025-03-31 paper.tex
First section of formalised availabilty

\section{Availability of source code and requirements}

The VCF Zarr specification is available on GitHub at
\url{https://github.com/sgkit-dev/vcf-zarr-spec/}.
The SAIGE prototype is available at \url{https://github.com/Will-Tyler/SAIGE}
and all other code for running benchmarks, analyses and creating
plots in this article is available at
\url{https://github.com/sgkit-dev/vcf-zarr-publication}.
Vcf2zarr is freely available under the terms of the Apache 2.0
license as part of the \texttt{bio2zarr}
suite (\url{https://github.com/sgkit-dev/bio2zarr/}; 
biotoolsID=bio2zarr; RRID=SCR\_026481)
and can be installed from the Python Package Index
(\url{https://pypi.org/project/bio2zarr/}).
Vcztools (\url{https://github.com/sgkit-dev/vcztools/};
biotoolsID=vcztools; RRID=SCR\_026482)
is freely available under the terms of the Apache 2.0
license and can be installed from the Python Package Index
(\url{https://pypi.org/project/vcztools/}).

>>>>

\section{Availability of source code and requirements}
\subsection{GitHub repository vcf-zarr-spec}
\begin{description}
\item[Project name:]  vcf-zarr-spec
\item[Github link:] https://github.com/sgkit-dev/vcf-zarr-spec/
\item[Operating system(s):] Platform independent
\item[Programming language:] NA
\item[License:] Apache-2.0
\item[Software Heritage PID:]
swh:1:snp:9f25395ea05afd4fc29912dcbf0e21d879f5cfee \cite{vcfzarr-spec-swh}
\end{description}

% \end{itemize}

% The VCF Zarr specification is available on GitHub at
% \url{https://github.com/sgkit-dev/vcf-zarr-spec/}.
% The SAIGE prototype is available at \url{https://github.com/Will-Tyler/SAIGE}
% and all other code for running benchmarks, analyses and creating
% plots in this article is available at
% \url{https://github.com/sgkit-dev/vcf-zarr-publication}.
% Vcf2zarr is freely available under the terms of the Apache 2.0
% license as part of the \texttt{bio2zarr}
% suite (\url{https://github.com/sgkit-dev/bio2zarr/}; 
% biotoolsID=bio2zarr; RRID=SCR\_026481)
% and can be installed from the Python Package Index
% (\url{https://pypi.org/project/bio2zarr/}).
% Vcztools (\url{https://github.com/sgkit-dev/vcztools/};
% biotoolsID=vcztools; RRID=SCR\_026482)
% is freely available under the terms of the Apache 2.0
% license and can be installed from the Python Package Index
% (\url{https://pypi.org/project/vcztools/}).
